US President Prediction

### 2024-11-04 paper/paper.qmd

## Model Check {#sec-model-check}

@@

## Model Diagnostics {#sec-result-diagnostics}
The model diagnostics indicate a strong fit and reliable predictive performance for both candidates, as detailed in the plots in the model section @sec-model-check. Posterior predictive checks ( @fig-harrisposcheck_1, @fig-harrisposcheck_2, @fig-trumpposcheck_1, and @fig-trumpposcheck_2) show that the predicted values align well with the observed data, suggesting that the models effectively capture key data patterns. Furthermore, the comparison of posterior and prior variables indicates minimal deviation, affirming an appropriate choice of priors. The credible intervals for the predictors (@fig-CIHarris and @fig-CITrump) encompass the observed support rates, demonstrating that the models adequately account for uncertainty in their predictions.

@@

# References {#sec-reference}

>>>>

@@

## Model Diagnostics {#sec-result-diagnostics}
The model diagnostics indicate a strong fit and reliable predictive performance for both candidates, as detailed in the plots in the appendix section @sec-app-M. Posterior predictive checks ( @fig-harrisposcheck_1, @fig-harrisposcheck_2, @fig-trumpposcheck_1, and @fig-trumpposcheck_2) show that the predicted values align well with the observed data, suggesting that the models effectively capture key data patterns. Furthermore, the comparison of posterior and prior variables indicates minimal deviation, affirming an appropriate choice of priors. The credible intervals for the predictors (@fig-CIHarris and @fig-CITrump) encompass the observed support rates, demonstrating that the models adequately account for uncertainty in their predictions.

@@

## Appendix 3 - Model validation plots {#sec-app-M}

\newpage
# References {#sec-reference}
